\bf\mftitle

### 2011-01-26 doc/jInfer/basicxsd/basicxsd.tex
Part of BasicXSDExporter documentation.

\def\mftitle{jInfer BasicDTDExporter Module Description}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

\begin{document}
\maketitle
\noindent Target audience: developers willing to extend jInfer, specifically hack the DTD export.

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Matej Vitásek \\ \hline
Required tokens:       & none \\ \hline
Provided tokens:       & cz.cuni.mff.ksi.jinfer.base.interfaces.inference.SchemaGenerator \\ \hline
Module dependencies:   & Base \\ \hline
Public packages:       & none \\ \hline
\end{tabular}

@@

This is a relatively simple implementation of a \jmodule{SchemaGenerator} exporting the inferred schema to DTD.

@@

The main class implementing \code{SchemaGenerator} inference interface and simultaneously registered as its service provider is \code{SchemaGeneratorImpl}. Its \code{start} method first topologically sorts all rules (elements) it got in the simplified grammar on input. This toposorting is necessary to avoid using anything not yet defined in the resulting schema. Afterwards, it creates their DTD string represenation.\\

Export of a single element is handled in the \code{elementToString()} method. First the actual \code{<!ELEMENT \ldots>} tag is exported, after that its attributes in a \code{<!ATTLIST \ldots>} tag (if there are any).

\subsection{Element content export}

TODO anti

\subsection{Attribute export}

>>>>

\def\mftitle{jInfer BasicXSDExporter Module Description}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

\begin{document}
\maketitle
\noindent Target audience: developers willing to extend jInfer, specifically hack the XSD export.

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Mário Mikula \\ \hline
Required tokens:       & none \\ \hline
Provided tokens:       & cz.cuni.mff.ksi.jinfer.base.interfaces.inference.SchemaGenerator \\ \hline
Module dependencies:   & Base \\ \hline
Public packages:       & none \\ \hline
\end{tabular}

@@

This is an implementation of a \jmodule{SchemaGenerator} exporting the inferred schema to XSD, providing basic features of the language.

@@

The main class implementing \code{SchemaGenerator} inference interface and simultaneously registered as its service provider is \code{SchemaGeneratorImpl}. Process of export consists of two phases described in detail in later sections:
\begin{enumerate}
	\item Preprocessing
	\item Own export to string representation of XSD
\end{enumerate}
Method \code{start} first creates instance of \code{Preprocessor} class supplied by rules (elements) it got in the simplified grammar on input. Phase of preprocessing is done by creating that instance (calling its constructor) and its purpose is to discover information such which elements should be globally defined and which element is the top level element (TODO rio how is this element called in XML??).\\

Afterwards, it recursively traverses global elements followed by other elements starting at the top level element and for each it creates element's XSD string representation.\\

\subsection{Preprocessing}

TODO rio

\subsection{Own export}

TODO rio\\
